
\documentclass[11pt]{article}
\usepackage{softwarespec}
\projectname{Lifting Bridges}

\title{Project Specification for 59-north.com Mapbox integration}

\author{Jordan Bettis}

\date{\today{}}
\documentnumber{59-NORTH-01}

\begin{document}

\maketitle
\tableofcontents

\newpage

\def\theclientprinciple{Andy Schell}
\def\theclient{59-North LLC}
\def\theclientaddress{1169 Hilltop Rd.\\Leesport, PA 19533}

\section{Introduction}

The goal of this project is to enable employees of \theclient{} to add
dynamic maps on 59-North.com, with custom route and destination
annotations, when creating or editing trip pages in the squarespace
admin.

This is to replace an existing workflow in which custom static image
assets are created for each trip, and to make the trip page visuals
more interactive.

\subsection{Deliverables}

\begin{description}

\item[Custom Map Design] A customization of the Mapbox \emph{North
  Star} map theme using a color palette complementary to that on 59-north.com.

\item[Custom Squarespace Theme] A custom variation of the \emph{SHIFT}
  template from Squarespace, that supports activation of a Mapbox map
  when the approprate data is included in a \texttt{code} block.

\item[Training and Assistance] Training on how to use the code block,
  format map path information into the JSON format, and make required
  changes to the Mapbox and Squarespace accounts.


\end{description}

\section{Components}

\subsection{Custom Map Design}

The Mapbox \emph{North Star} theme includes bathymetric features and
nautical styling. The default color scheme does not match the color
scheme of 59-north.com. The provider will modify the color scheme of
the \emph{North Star} theme, using the existing color scheme of 59-north.com.

\emph{This component will cost \$240.00}

\subsection{Custom Squarespace Theme}

When a map is embeded in a website, a variety of metadata must be
provided to the embedded widget including:

\begin{itemize}

\item widget size and placement,
\item map coordinate centroid and zoom level, and
\item path and point data for dynamic map features.
  
\end{itemize}

The contractor will modify the \emph{SHIFT} theme to include logic to
handle size and placement, as well as to minimize the amount of code
that will need to be provided through the squarespace admin to set
centroid, zoom, and path and point data.

Dynamic map features include custom path elements the client can
use to draw the boat's route along each leg of a trip, and custom point
elements that the client can use for destinations and ports-of-call.
The points will be clickable and the client will be able to include
custom text that will appear in map popup elements when clicked.

This component will also include the creation of sample code for the
snippet that must be provided through the squarespace admin.

\emph{This component will cost \$1280.00}

\subsection{Training and Assistance}

The contractor will provide 6 hours of assistence and training to the
client in order to insure that they can successfully:

\begin{itemize}

\item activate the modified map theme in their mapbox account,
\item activate the custom site theme in their squarespace account,
\item format trip information into structured point and path data using the JSON format, and
\item include them in the code snippet to activate the map and required dynamic features.

\end{itemize}

Training will include communications by telephone, screen share, and
possibly email.

\emph{This component will cost \$480.00}

\section{Business Relationship}

\subsection{Definitions}
\label{definitions}

\begin{description}

\item[Lifting Bridges, Ltd] An Illinois S-Corporation. All references
  to ``Lifting Bridges,'' ``the Provider'' or ``the Contractor'' in
  this document shall refer to Lifting Bridges, Ltd.

\item[\theclient] The organization commissioning the development of
  the project. All references to ``the Client'' in this document shall
  refer to \theclient.

\item[Mapbox Inc] A third-party service provider.

\item[Squarespace Inc] A third-party service provider.

\end{description}

\subsection{Intellectual Property}

Any inventions, discoveries, developments or innovations conceived by
the provider directly in the course of fulfilling this contract shall
become the property of the client upon receipt of full payment of the
applicable invoice to the provider.

However, any inventions, discoveries, developments or innovations
conceived by the provider prior to, subsequent to, or during the term of
the contract, not conceived directly in the course of fulfilling the
contract, shall remain the property of the provider, the provider's
successors, or the provider's assigns.

\subsection{Payment}

Payment shall be provided in-kind (\$2000.00 discount on services
provided by \theclient).

\subsection{Billing Terms}

The client shall make full payment of each invoice within fifteen days
of the issue date. 

Payment may be made by any legal negotiable instrument at the
convenience of the client, provided that instrument has the value
prescribed in this document at point when it is converted by the
provider.

\subsection{Successors}

All provisions of this contract shall be binding upon the successors or
assigns of both parties.

\subsection{Third Party Services}

The business relationship with all third-party service providers or
subcontractors are the sole responsiblity of \theclient. Lifting
Bridges Ltd does not warrantee any service or goods provided by
third party providers nor does the provider offer any indemnefication
for losses resulting from the actions of third party providers.

\subsection{Venue}

Both parties shall agree to hold any action concerning breach of this
agreement in the Circuit Court of Cook County, Illinois, or the United
States District Court of Northern Illinois, Eastern Division. The
validity of the agreement shall be governed by the laws of the State
of Illinois without regard to any applicable conflicts-of-laws rules.

\subsection{Severability}

Should any part of this agreement be found illegal, invalid, or
unenforceable the remainder of the agreement shall remain in full force
and effect.

\newpage
\section{Counterpart Signatures}

This agreement must be signed by the representative of both the
provider and the client. Electronic facsimiles shall be treated as
original signatures.

\vspace{2in}
\hspace{-.25in}\rule{3.5in}{.2mm} Date: \rule{1.5in}{.2mm}\\
\vspace{0.2em}
Jordan Bettis\\
Lifting Bridges Ltd\\
PO Box 471388\\
Chicago, IL 60647\\
(312) 628-5508

\vspace{2in}
\hspace{-.25in}\rule{3.5in}{.2mm} Date: \rule{1.5in}{.2mm}\\
\vspace{0.2em}
\theclientprinciple\\
\theclient\\
\theclientaddress{}

\end{document}
